Code for Submission

### 2023-06-07 CodeForSubmission.Rmd
Removed author info from code.
Addedd faceted Fig. 4 option

Authors: Anna Parker and Joel Kingsolver

@@

Make new dataframes
```{r}
datalong5 <- data %>%
  select(ID, food, fate, mass.max, ttmax, area)

@@

>>>>

@@

Make new dataframes
```{r}
datalong5 <- data %>%
  select(ID, food, treatment, fate, mass.max, ttmax, area)

@@

```{r}
datalong5$treatment <- factor(datalong5$treatment, labels = c("Nonparasitized baseline", "Nonparasitized heat shocked", "Parasitized baseline", "Parasitized heat shocked"))

newmeansfacet <- ggplot(data = datalong5, aes(x = ttmax, y = mass.max, color = fate, shape = food)) + 
  facet_wrap(~ treatment) + 
  theme_bw() + 
  xlim(15, 45) +
  ylim(0, 20) + 
  geom_point(alpha = 0.8) + 
  scale_shape_manual(values = c(1, 19)) + 
  scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60"), 
                     labels = c("Wander", "WE", "Small WOWE", "Large WOWE")) + 
#  geom_point(aes(x = ttmax, y = mass.max, color = fate, shape = food), data = datameans2, size = 4) + 
#  geom_errorbar(data = datameans2, aes(ymin = mass.max - semass, ymax = mass.max + semass), size = .5) + 
#  geom_errorbarh(data = datameans2, aes(xmin = ttmax - se, xmax = ttmax + se), size = .5) + 
#  guides(size = FALSE) + 
  labs(x = "Age at maximum mass (days)", y = "Maximum mass achieved (g)", 
       shape = "Hostplant Consumed", color = "Developmental Outcome")

newmeansfacet
```
